Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-07-06 paper/ms.tex
flash->FLASH.
citet->citep

The C-O and C-O-Ne models have the same central temperature
and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
The C-O-Ne model used in flash had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.

@@

The ignition of the deflagration via a match head followed the
initialization described in~\citet{Kruegeretal2012}, which
followed the method of~\citet{townetal2009}.
In both the hybrid and traditional cases, the match head had a
nominal radius of $150$~km before
a different randomly-seeded perturbation was applied to the
match head for each of the 30 simulations in both suites,
The perturbation to the sphere's surface is a set of
spherical harmonic functions with randomly chosen amplitudes, and
each set of perturbations is referred to as a ``realization."
Both suites use the same 30 realizations of the ignition geometry.
These perturbations have been shown to reproduce
the scatter in \Ni{56}
yield from \SNeIa\ \citet{townetal2009}.

>>>>

The C-O and C-O-Ne models have the same central temperature
and density, $8.2\times 10^8$~K and $2.2\times 10^9$~g~cm$^{-3}$ respectively.
The C-O model's composition consisted of \C{12}, \Ox{16}, and \Ne{22} in mass fractions 0.4, 0.57, and 0.02 respectively in the convective core and 0.5, 0.48, and 0.02 outside the convective core.
The C-O-Ne model used in \FLASH\ had composition consisting of \C{12}, \Ox{16}, \Ne{20}, and \Ne{22}.
The mass fractions in the central convection zone were 0.14, 0.68, 0.23, and 0.05 respectively, and vary smoothly outside the convection zone as shown in Figure~\ref{fig:init_conds}.

@@

The ignition of the deflagration via a match head followed the
initialization described in~\citet{Kruegeretal2012}, which
followed the method of~\citet{townetal2009}.
In both the hybrid and traditional cases, the match head had a
nominal radius of $150$~km before
a different randomly-seeded perturbation was applied to the
match head for each of the 30 simulations in both suites,
The perturbation to the sphere's surface is a set of
spherical harmonic functions with randomly chosen amplitudes, and
each set of perturbations is referred to as a ``realization."
Both suites use the same 30 realizations of the ignition geometry.
These perturbations have been shown to reproduce
the scatter in \Ni{56}
yield from \SNeIa\ \citep{townetal2009}.
